### 2019-09-27 conflog.tex

Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities. 
\begin{center}
	\begin{tabular}{l r}
	\hline\hline
	\textbf{School}& \textbf{Drive Time}\\
	\hline\hline
	U. Tennessee Knoxville & 7 h 13 min\\
	University of Michigan & 5 h 24 min\\
	Clemson University & 10 h 5 min\\
	U. Missouri-Columbia & 4 h 18 min\\
	Georgia Tech University & 8 h 54 min \\
	University of Pittsburgh & 7 h 19 min\\
	U. Wisconsin-Madison & 3 h 53 min \\
	Penn State University & 9 h 17 min\\
	University of South Carolina& 10 h 44 min\\
	Iowa State University & 5 h 24 min \\
	University of Iowa & 3 h 34 min\\
	Vanderbilt University & 5 h 18 min\\
	\end{tabular}
\end{center}

>>>>

Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities.

\begin{center}
   \begin{tabular}{lcccc}
   \hline\hline
   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost}&\textbf{Per Person}\\
   \hline\hline
    Purdue University&90&1h 40m&\$21.86&\$5.47\\
    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
    University of Wisconsin&253&4h&\$61.46&\$15.36\\
    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
    \hline
    Average&279&4h 22m&\$67.87&\$16.97

    \end{tabular} 
\end{center}
